Dirac neutrino mass generation from Majorana messenger

### 2019-09-20 draft.tex
Updates from Overleaf

\author{Julian Calle${}^1$\footnote{\href{mailto:julian.callem@udea.edu.co}{julian.callem@udea.edu.co}},
  Diego Restrepo${}^{1,2}$\footnote{\href{mailto:restrepo@udea.edu.co}{restrepo@udea.edu.co}}, and Óscar Zapata${}^1$\footnote{\href{mailto:oalberto.zapata@udea.edu.co }{oalberto.zapata@udea.edu.co}}\\
[2mm]  
\textit{\small ${}^1$Instituto de Física,
  Universidad de Antioquia,
}\\
\textit{\small   Calle 70 \# 52-21, Apartado Aéreo 1226, Medellín, Colombia.}\\
[2mm]
\textit{\small ${}^2$
International Institute of Physics, Universidade Federal do Rio Grande do Norte,
}\\
\textit{\small Campus Universitario, Lagoa Nova, Natal-RN 59078-970, Brazil. }
}
\date{\small September DD, 2019}
\begin{document}
\maketitle
\ReportNumbers{IIPDM-2019}

@@

\section*{Acknowledgments}
Work supported by Sostenibilidad-UdeA and the UdeA/CODI Grant
2017-16286, and by COLCIENCIAS through the Grant 111577657253. D.R
would also like to thank the IIP-Natal, for its support,
hospitality and the nice and stimulating atmosphere during the
Visiting Professors program where part of this work was completed.
\appendix
\section{$\operatorname{U}(1)_X$ anomaly cancellation }
We use $f$ ($f$) to denote the general $\operatorname{U}(1)_X$ generation-independent charge assignments of the field $f_R$ ($F_L$). The three linear anomalies in $\operatorname{U(1)_X}$~\cite{Campos:2017dgc}
\begin{align}
  \label{eq:anolin}
  \left[\mathrm{SU}(3)_{C}\right]^{2} \mathrm{U}(1)_{X} :& &
[3 u+3 d]-[3 \cdot 2 q]=&0, \nonumber\\
\left[\mathrm{SU}(2)_{L}\right]^{2} \mathrm{U}(1)_{X} :&&
-[2 l+3 \cdot 2 q]=&0, \nonumber\\
\left[\mathrm{U}(1)_{Y}\right]^{2} \mathrm{U}(1)_{X} :&&
{ \left[(-2)^{2} e+3\left(\tfrac{4}{3}\right)^{2} u+3\left(-\tfrac{2}{3}\right)^{2} d\right]-\left[2(-1)^{2} l+3 \cdot 2\left(\tfrac{1}{3}\right)^{2} q\right]}=&
 0,
  \end{align}
allows to express three $X$-charges in terms of the other two
\begin{align}
  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
\end{align}
The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos. For $N$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
\begin{align}
  \left[\text{Grav}\right]^{2} \mathrm{U}(1)_{X}:\ \sum_{\alpha=1}^N n_{\alpha}+3 (e-2l)=&0\,, &  \left[\mathrm{U}(1)_{X}\right]^{3}:\ \sum_{\alpha=1}^N n_{\alpha}^3+3 (e-2l)^3=&0\,. &
\end{align}
We choose the solutions with $r\equiv e-2l$, such that
\begin{align}
  \label{eq:anolam}
  \sum_{\alpha=1}^{N} n_{\alpha}=&-3 r\,,   & \sum_{\alpha=1}^{N} n_{\alpha}^3=&-3 r^3\,.
\end{align}
The full set of anomaly free standard model $X$-charges in terms of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc} that we choose as $l$ and $r$, is just
\begin{align}
  u=&-r-\frac{4l}{3}\,,&d=&r+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&r+2l\,,&h=&-r-l\,.
  \label{Eq:SMCharges}
\end{align}
By setting $l=0$ in the previous equations, we can define the Abelian symmetry in which only the right-handed charged fermions have non-vanishing $X$-charges as $\operatorname{U}(1)_R$. Then the general anomaly free two-parameter solution can be written as
\begin{align}
  X(r,l)=r R- l Y\,.
\end{align}

>>>>

\author{Julian Calle${}^1$\footnote{\href{mailto:julian.callem@udea.edu.co}{julian.callem@udea.edu.co}},
  Diego Restrepo${}^{1,2}$\footnote{\href{mailto:restrepo@udea.edu.co}{restrepo@udea.edu.co}}, and Óscar Zapata${}^1$\footnote{\href{mailto:oalberto.zapata@udea.edu.co }{oalberto.zapata@udea.edu.co}}\\
[2mm]  
\textit{\small ${}^1$Instituto de Física,
  Universidad de Antioquia,
}\\
\textit{\small   Calle 70 \# 52-21, Apartado Aéreo 1226, Medellín, Colombia.}\\
[2mm]
\textit{\small ${}^2$
International Institute of Physics, Universidade Federal do Rio Grande do Norte,
}\\
\textit{\small Campus Universitario, Lagoa Nova, Natal-RN 59078-970, Brazil. }
}
\date{\small September 23, 2019}
\begin{document}
\maketitle
\ReportNumbers{IIPDM-2019}

@@

\section*{Acknowledgments}
Work supported by Sostenibilidad-UdeA and the UdeA/CODI Grant
2017-16286, and by COLCIENCIAS through the Grant 111577657253. D.R
would also like to thank the IIP-Natal, for its support,
hospitality and the nice and stimulating atmosphere during the
Visiting Professors program where part of this work was completed.
\appendix
\section{$\operatorname{U}(1)_X$ anomaly cancellation }
We use $f$ ($f$) to denote the general $\operatorname{U}(1)_X$ generation-independent charge assignments of the field $f_R$ ($F_L$). The three linear anomalies in $\operatorname{U(1)_X}$~\cite{Campos:2017dgc}
\begin{align}
  \label{eq:anolin}
  \left[\mathrm{SU}(3)_{C}\right]^{2} \mathrm{U}(1)_{X} :& &
[3 u+3 d]-[3 \cdot 2 q]=&0, \nonumber\\
\left[\mathrm{SU}(2)_{L}\right]^{2} \mathrm{U}(1)_{X} :&&
-[2 l+3 \cdot 2 q]=&0, \nonumber\\
\left[\mathrm{U}(1)_{Y}\right]^{2} \mathrm{U}(1)_{X} :&&
{ \left[(-2)^{2} e+3\left(\tfrac{4}{3}\right)^{2} u+3\left(-\tfrac{2}{3}\right)^{2} d\right]-\left[2(-1)^{2} l+3 \cdot 2\left(\tfrac{1}{3}\right)^{2} q\right]}=&
 0,
  \end{align}
allows to express three $X$-charges in terms of the other two
\begin{align}
  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
\end{align}
The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos. For $N$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
\begin{align}
  \left[\text{Grav}\right]^{2} \mathrm{U}(1)_{X}:\ \sum_{\alpha=1}^N n_{\alpha}+3 (e-2l)=&0\,, &  \left[\mathrm{U}(1)_{X}\right]^{3}:\ \sum_{\alpha=1}^N n_{\alpha}^3+3 (e-2l)^3=&0\,. &
\end{align}
We choose the solutions with $r\equiv e-2l$, such that
\begin{align}
  \label{eq:anolam}
  \sum_{\alpha=1}^{N} n_{\alpha}=&-3 r\,,   & \sum_{\alpha=1}^{N} n_{\alpha}^3=&-3 r^3\,.
\end{align}
The full set of anomaly free standard model $X$-charges in terms of two parameters~\cite{Appelquist:2002mw,Campos:2017dgc} that we choose as $l$ and $r$, is just
\begin{align}
  u=&-r-\frac{4l}{3}\,,&d=&r+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&r+2l\,,&h=&-r-l\,.
  \label{Eq:SMCharges}
\end{align}
where the condition in the charged lepton Yukawa couplings have been used to fix $h$, and is automatically consistent with the conditions in the quark Yukawa couplings. By setting $l=0$ in the previous equations, we can define the Abelian symmetry in which only the right-handed charged fermions have non-vanishing $X$-charges as $\operatorname{U}(1)_R$. Then the general anomaly free two-parameter solution can be written as
\begin{align}
  X(r,l)=r R- l Y\,.
\end{align}
